Baseline centering problem

### 2018-12-12 paper/tangotd.tex

This contains: Section 1: remarks on recovering the known convergence results
for TD in a single framework, plus ideas on systematic variants around
two-timescale algorithms or improved ``almost-one-timescale'' algorithms.

Section 2: the problem of the existence of near-solutions to the Bellman
equation that are very far from the true value function (I think this is
quite serious off-policy).

Section 3: Ideas on how, even if there's no reward signal, we should
still learn how to navigate in the Markov chain and learn which
actions/policy to use to go to which states. This extends eligibility
traces in a systematic way.

\section{Recovering known convergence results for TD, and a few ideas}

@@

\paragraph{Minimizers of errors.} Rather than the fixed point of TD, one
can look for minimizers of the error in various norms.

@@

\paragraph{Double sampling problem: using a model for one of the
samples.} Double sampling allows us to minimize the $L^2$ norm of the
Bellman gap. This is only possible if we have model of the environment,
that allows for sampling $s'$ given $s$ and $a$.

@@

\section{A function that almost solves the Bellman equation can be very
far from the true value function}

@@

\section{Storing a summary of possible transitions?}

>>>>

This contains: Section~\ref{sec:tdconv}: remarks on recovering the known convergence results
for TD in a single framework, plus ideas on systematic variants around
two-timescale algorithms or improved ``almost-one-timescale'' algorithms.

Section~\ref{sec:norms}: algorithms for convergence of the Bellman error
in various norms. In particular, solving the double sampling problem by
using a model for one of the samples, and a real transition for the other
sample, has nice mathematical properties.

Section~\ref{sec:quasibellman}: the problem of the existence of near-solutions to the Bellman
equation that are very far from the true value function (I think this is
quite serious off-policy).

Section~\ref{sec:green}: Ideas on how, even if there's no reward signal, we should
still learn how to navigate in the Markov chain and learn which
actions/policy to use to go to which states. This extends eligibility
traces in a systematic way.

\section{Recovering known convergence results for TD, and a few ideas}
\label{sec:tdconv}

@@

\section{Minimizing the error in some norm via TD}
\label{sec:norms}

Rather than the fixed point of TD, one
can look for minimizers of the error in various norms.

@@

\paragraph{Double sampling: using a model for one of the
samples.} Double sampling allows us to minimize the $L^2$ norm of the
Bellman gap. This is only possible if we have model of the environment,
that allows for sampling $s'$ given $s$ and $a$.

@@

\section{A function that almost solves the Bellman equation can be very
far from the true value function}
\label{sec:quasibellman}

@@

\section{Storing a summary of possible transitions?}
\label{sec:green}
